# Self Controlled Cohort Analysis

## Methods

The self-controlled cohort method estimates the association between an exposure
(drug) and an outcome by comparing the outcome rate while a person is exposed
to the outcome rate while that same person is unexposed (self controlled).  For
each database the exposure - outcome pairs produce an incidence rate ratio.
Where multiple databases contribute results an evidence synthesis (meta
analysis) is performed across the databases.  The estimates shown below have
been empirically calibrated using negative control exposure-outcome pairs where
possible.

## Results

```{r}
#| label: scc_extract
#| echo: false
#| include: false

sccSchema <- params$schema

sccSignals <- tryCatch(
  OhdsiReportGenerator::getSccSignals(
    connectionHandler = connectionHandler,
    schema = sccSchema,
    minBenefitSources = 0,
    maxRiskSources = 999
  ),
  error = function(e) {
    return(data.frame())
  }
)

sccEstimation <- tryCatch(
  OhdsiReportGenerator::getSccEstimation(
    connectionHandler = connectionHandler,
    schema = sccSchema
  ),
  error = function(e) data.frame()
)

sccMeta <- tryCatch(
  OhdsiReportGenerator::getSccMetaEstimation(
    connectionHandler = connectionHandler,
    schema = sccSchema
  ),
  error = function(e) data.frame()
)

sccDiagnostics <- tryCatch(
  OhdsiReportGenerator::getSccDiagnosticsData(
    connectionHandler = connectionHandler,
    schema = sccSchema
  ),
  error = function(e) data.frame()
)

sccStats <- tryCatch(
  OhdsiReportGenerator::getSccSummaryStats(
    connectionHandler = connectionHandler,
    schema = sccSchema
  ),
  error = function(e) data.frame()
)

if (nrow(sccEstimation) > 0) {
  sccEstimation$meta <- 0
}
if (nrow(sccMeta) > 0) {
  sccMeta$meta <- 1
}
sccParts <- list()
if (nrow(sccEstimation) > 0) {
  sccParts[[length(sccParts) + 1]] <- sccEstimation
}
if (nrow(sccMeta) > 0) {
  sccParts[[length(sccParts) + 1]] <- sccMeta
}
sccCombined <- if (length(sccParts) > 0) {
  dplyr::bind_rows(sccParts)
} else {
  data.frame()
}

if (nrow(sccSignals) == 0 || nrow(sccCombined) == 0) {
  includeSccResults <- FALSE
} else {
  includeSccResults <- TRUE
}
```

```{r}
#| label: scc_results
#| echo: false
#| results: 'asis'

if (includeSccResults) {
  cat("\n\n### Discovery results\n\n")
  signalTable <- OhdsiReportGenerator::createSccSignalsTable(sccSignals)
  if (!is.null(signalTable)) {
    print(signalTable)
  }

  cat("\n\n### Pair level results\n\n")
  for (i in seq_len(nrow(sccSignals))) {
    row <- sccSignals[i, ]
    pairData <- sccCombined[sccCombined$targetId == row$targetId &
                              sccCombined$outcomeId == row$outcomeId, , drop = FALSE]
    if (nrow(pairData) == 0) {
      next
    }

    title <- paste0(row$targetName, " - ", row$outcomeName)
    cat(paste0("\n::: {.callout-note collapse='true'}\n### ", title, "\n\n"))

    cat("The forest plot shows the per database incidence rate ratios with the
    meta analytic result shown as a diamond.\n\n")

    plot <- OhdsiReportGenerator::plotSccForest(pairData, calibrated = TRUE)
    if (!is.null(plot)) {
      print(plot)
    }

    pairStats <- sccStats[sccStats$targetId == row$targetId &
                            sccStats$outcomeId == row$outcomeId, , drop = FALSE]
    if (nrow(pairStats) > 0) {
      boxPlot <- OhdsiReportGenerator::plotSccBoxPlot(pairStats)
      if (!is.null(boxPlot)) {
        print(boxPlot)
      }
    }

    pairDiag <- sccDiagnostics[sccDiagnostics$targetId == row$targetId &
                                 sccDiagnostics$outcomeId == row$outcomeId, , drop = FALSE]
    if (nrow(pairDiag) > 0) {
      diagSummary <- pairDiag |>
        dplyr::select(
          "databaseName", dplyr::any_of(
            c("mdrr", "ease", "preExposurePValue", "summaryValue")
          )
        ) |>
        gt::gt()
      print(diagSummary)
    }

    cat("\n:::\n")
  }
}
```
